---
title: "dalarre_PeerCommentary_mrubiog2000"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#CHALLENGE 1

```{r}
v<-c("Stately,", "plump", "Buck", "Mulligan", "came", "from", "the", "stairhead,", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a",  "razor", "lay", "crossed.")

v[c(3, 6, 9, 12, 15, 18, 21)]

#I have selected the words in postitions that are multiple of 3
```

Peer commentary for challenge 1:

The challenge is correctly achieved, so this code is perfectly right. But if you want there are some functions that allow to write this in a more concise way.
    - You could use v[seq()], which allows you to call the elements every x position instead of calling a vector containing every 3rd position
    - If you want to use the stringr package (I saw that that was one of your issues in the section challenges) you can do the following (This also allows you to not need to separate every word in the sentence in your vector v):

```{r}
v <- c("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.")
w <- stringr :: str_split(v, pattern = " ")
names(w) <- c("string")
w <- gsub("[[:punct:]]","",w$string)
w[seq(from = 1 , to = 22, by = 3)]

```
I don't know if this is the most efficient way to do it but it worked for me. The str_split function divides the vector v in words (divides every " "). However, I don't know why but this separate words are stored as a vector inside of a list, so in order to interact with it you have to name it. After that, the gsub function removes punctuation and special characters, and the words get stored as a vector outside a list again. To end, you call every 3rd element of this new vector using the seq function.
Using the stringr package in this challenge isn't more concise than what you did, but I believe that if you have a larger sentence or text it is useful to use it.


#CHALLENGE 2

```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)

a<-m[,2]
b<-m[,3]
c<-m[,6]
#First I extract each of the asked columns from the matrix and create a vector with the values of each column.

x<-c(a, b, c)
#Second I create another vector called "x" that contains the vectors "a", "b" and "c".
x
```

```{r}
d<-m[6,]
e<-m[8,]
x<-c(d, e)
#Same as above
```

#CHALLENGE 3

```{r}
a<-array(data=400:1, dim=c(5, 5, 4, 4))
a

a[1, 1, 1, 2]#Slection of the values in row 1, column 1, level 1 and level set 2.
a[2, 3, 2, ] #Selection of the values in row 2, column 3 and level 2 from every level set.
a[1:5, 1:5, 3, 3] #Selection of the values from row and column 1-5 from level 3 of the level set 3.
```

"Overwriting" 

```{r}
m[7, 1] <- 564
#The value from row 7, column 1 is now the value "564".
m[, 8] <- 2
#In every row, the values from column 8 are now the value "2".
m[2:5, 4:8] <- 1
#The values from the rows 2 to 5 and from the columns 4 to 8 are now the value "1".
m[2:5, 4:8] <- c(20, 19, 18, 17)
#The values from the rows 2 to 5 and from the columns 4 to 8 are substitued for the values from vector "c".
m[2:5, 4:8] <- matrix(data = c(20:1), nrow = 4, ncol = 5, byrow = TRUE)
#The values from the rows 2 to 5 and from the columns 4 to 8 of the matrix called "m" are substituted for the values from a new matrix called "matrix" with 4 rows and 5 columns. "matrix" contains values from 20 to 1 (descending order) ordered by rows.
m[, 8] <- c("a", "b")
#The values from column 8 are substituted for a vector that has two characters: "a" and "b". As there are 8 rows in the matrix and the vector only contains 2 values, "a" and "b" are repeated.
```


#CHALLENGE 4

```{r}
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
#This part is in the website: list called "Strepsirhini" that contains the vectors "Lemuroidea" and "Lorisoidea"


Catarrhini<-c("Cercopithecidae", "Hylobatidae", "Hominidae")
Platyrrhini<-c("Cebidae", "Atelidae", "Pitheciidae")
Anthropoidea<-list(Catarrhini, Platyrrhini)
names(Anthropoidea)<-list("Catarrhini", "Platyrrhini")
#List called "Anthropoidea" that includes the 2 vectors "Catarrhini" and "Platyrrhini".

Tarsioidea<-c("Tarsiidae")
Haplorhini<-list(Anthropoidea, Tarsioidea)
names(Haplorhini)<-list("Anthropoidea", "Tarsioidea")
#List called "Haplorhini" that contains the list "Anthropoidea" and the vector "Tarsioidea".

Primates<-list(Haplorhini, Strepsirhini)
names(Primates)<-list("Haplorhini", "Strepsirhini")
#List called "Primates" that contains the list "Haplorhini" and "Strepsirhini".

Primates
```

#CHALLENGE 5

```{r}
m3<-matrix (data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow=5, ncol=3, byrow=TRUE)

df<-data.frame(m3)
as.logical(df[,2]) #I am indicating that the values from column 2 of the data frame become logical values.

as.factor(df[,3]) #I am indicating that the values from column 3 of the data frame become factor values (1 or 2).
str(df)
```

#CHALLENGES

#The most difficult parts to me were:
  
  -Trying to use the "stringr" package. Solution: I gave up and tried another way to solve the problem.
  
  -Reading and understanding the "Help" sections of R (package, function...). Solution: I red again the information for the module and tried different options of coding till I understood how to do it (in Challenge 5)
  
  -Finish Challenge 2. Solution: I could not find the way to do it directly, so I end up doing it by several steps.

  
