---
title: "mrubiog2000_FinalHomeworkCode_01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#CHALLENGE 1

```{r}
v<-c("Stately,", "plump", "Buck", "Mulligan", "came", "from", "the", "stairhead,", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a",  "razor", "lay", "crossed.")

v[seq(from=1, to=22, by=3)]

#I have used the "seq" function that allows to separate and select the elements you want from the vector. I got this idea from Zoe's Code (@zealbert).
```

#CHALLENGE 2

```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
x<-m[,c(2,3,6)]
x
#I have selected the columns in the matrix "m" directly instead of creating 3 different vector as Diego (@dalarre) told me during in his comments.
```

```{r}
x<-m[2:6, 2:9]
x
#Commenting Zoe's coding and reading Diego's comment I realised that I had this part wrong. I have selected from row 2 to row 6 and from column 2 to column 9, the same way as Zoe has (@zalbert).
```

#CHALLENGE 3

```{r}
a<-array(data=400:1, dim=c(5, 5, 4, 4))
a

a[1, 1, 1, 2]#Slection of the values in row 1, column 1, level 1 and level set 2.
a[2, 3, 2, ] #Selection of the values in row 2, column 3 and level 2 from every level set.
a[1:5, 1:5, 3, 3] #Selection of the values from row and column 1-5 from level 3 of the level set 3.
```

"Overwriting" 

```{r}
m[7, 1] <- 564
#The value from row 7, column 1 is now the value "564".
m[, 8] <- 2
#In every row, the values from column 8 are now the value "2".
m[2:5, 4:8] <- 1
#The values from the rows 2 to 5 and from the columns 4 to 8 are now the value "1".
m[2:5, 4:8] <- c(20, 19, 18, 17)
#The values from the rows 2 to 5 and from the columns 4 to 8 are substitued for the values from vector "c".
m[2:5, 4:8] <- matrix(data = c(20:1), nrow = 4, ncol = 5, byrow = TRUE)
#The values from the rows 2 to 5 and from the columns 4 to 8 of the matrix called "m" are substituted for the values from a new matrix called "matrix" with 4 rows and 5 columns. "matrix" contains values from 20 to 1 (descending order) ordered by rows.
m[, 8] <- c("a", "b")
#The values from column 8 are substituted for a vector that has two characters: "a" and "b". As there are 8 rows in the matrix and the vector only contains 2 values, "a" and "b" are repeated.
```


#CHALLENGE 4

```{r}
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
#This part is in the website: list called "Strepsirhini" that contains the vectors "Lemuroidea" and "Lorisoidea"


Catarrhini<-c("Cercopithecidae", "Hylobatidae", "Hominidae")
Platyrrhini<-c("Cebidae", "Atelidae", "Pitheciidae")
Anthropoidea<-list(Catarrhini, Platyrrhini)
names(Anthropoidea)<-list("Catarrhini", "Platyrrhini")
#List called "Anthropoidea" that includes the 2 vectors "Catarrhini" and "Platyrrhini".

Tarsioidea<-c("Tarsiidae")
Haplorhini<-list(Anthropoidea, Tarsioidea)
names(Haplorhini)<-list("Anthropoidea", "Tarsioidea")
#List called "Haplorhini" that contains the list "Anthropoidea" and the vector "Tarsioidea".

Primates<-list(Haplorhini, Strepsirhini)
names(Primates)<-list("Haplorhini", "Strepsirhini")
#List called "Primates" that contains the list "Haplorhini" and "Strepsirhini".

Primates
```

#CHALLENGE 5

```{r}
m3<-matrix (data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow=5, ncol=3, byrow=TRUE)

df<-data.frame(m3)
df[,2] = as.logical(df[,2]) #I am indicating that the values from column 2 of the data frame become logical values (TRUE or FALSE). I changed the code as Diego told me (@dalarre) so now the values from column 2 have really changed into logical values (the other way just SHOW them as logical values).

df[,3] = as.factor(df[,3]) #I am indicating that the values from column 3 of the data frame become factor values (1 or 2). I have changed it the same way as the code above.
str(df)
```

#CHALLENGES

#The most difficult parts to me were:
  
  -Trying to use the "stringr" package. Solution: I gave up and tried another way to solve the problem.
  
  -Reading and understanding the "Help" sections of R (package, function...). Solution: I red again the information for the module and tried different options of coding till I understood how to do it (in Challenge 5)
  
  -Finish Challenge 2. Solution: I could not find the way to do it directly, so I end up doing it by several steps.
